---
title: "Shiny Application and Reproducible Pitch"
author: "Chris Brueck"
date: "`r Sys.Date()`"
output: ioslides_presentation
---




## Course Project Description

This is the final course project for the Developing Data Products Coursera course

    Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.

    Deploy the application on Rstudio's shiny server

    Share the application link by pasting it into the provided text box

    Share your server.R and ui.R code on github


## How to use the application

With the Iris flower dataset, we plot the differences in Length and Width of the Petal and Sepal of Three Iris Species. 

The application is running on (https://brubru.shinyapps.io/MrPredictor/)

ui.R, and Server.R Code in my github repository (https://github.com/bru-dot-edu/DDP-W4-CourseProject)

## Iris Dataset

The data used in the app comes from the GaltonFamilies dataset. 

```{r summary}
library(datasets)
data(iris)
summary(iris)
```

## Plot
In the scatterplot below are represented the data used for plotting
```{r plot}
library(datasets)
data(iris)
plot(iris)
```